---
title: "Figures"
output: html_document
author: "Michael Chas Sumner"
---

## chunk0.1, setup packages and root.dir

```{r setup, include = F}

pull_dir <- "~/PULLS/R_sim_scripts/"

dataset_dir <- "~/DataSets/"

file_dir <- paste(dataset_dir, "/d201102/", sep = "")

library(stats)

library(data.table)

library(tidyverse)

library(gganimate)

library(gifski)

library(viridis)

library(knitr)

library(gridExtra)

source(paste(pull_dir, "Simulated_MSD.R", sep = ""), echo = FALSE)

source(paste(pull_dir, "smoothMSD.R", sep = ""), echo = FALSE)

source(paste(pull_dir, "SimLin_Repos.R", sep = ""), echo = FALSE)

source(paste(pull_dir, "multimsd.R", sep = ""), echo = FALSE)

uap <- "U3alonePlus"
gup <- "G1atU3Plus"

comtheme <- theme_bw() +
  theme(
    text = element_text(color = "#545454", size = 18),
    legend.position = "none"
  )

# set this to the raw_data directory
opts_knit$set(root.dir = paste(file_dir, sep = ""))
```




## chunk1, create list of trajectories as matrices

## if Debuffer = True, the matrices will be cropped to the size defined in
debuff_end and debuff_start

```{r, echo=F}

# Controls wheter you cut off the first specified number of steps for each trajectory
Debuffer <- F
remove_incomplete_trajectoreies <- T
expected_nrow <- 6000

list.files()

# specify the directory containing trajectory .csv files

list_source_wd <- list.files()[4]

print(list_source_wd)
setwd(list_source_wd)

list_source_wd <- getwd() %>%
  strsplit("/") %>%
  unlist()
list_source_wd <- list_source_wd[length(list_source_wd)]

print(list_source_wd)

for (i in 1:length(list.files())) {
  if (i == 1) {
    
    sim_list <- vector(mode = "list", length = length(list.files()))
  
  }
  
  sim_list[[i]] <- as.matrix(fread(list.files()[i]))

}

if (remove_incomplete_trajectoreies == T) {
  
  cleaned_list <- list()
  clean_position <- 0
  
  for (i in 1:length(sim_list)) {
    
    tail_check <- sim_list[[i]][nrow(sim_list[[i]]), ]
    
    if (is.na(tail_check[1]) | is.nan(tail_check[1]) | is.na(tail_check[2]) | is.nan(tail_check[2]) | sqrt(tail_check[1]^2 + tail_check[2]^2) > 1 | nrow(sim_list[[i]]) < expected_nrow) {
      
      print("NA NaN or Error detected")
      next
      
    } else {
      clean_position <- clean_position + 1
      
      cleaned_list[[clean_position]] <- sim_list[[i]]
    }
  }
  print(paste(length(cleaned_list), "/", length(sim_list)), sep = "")
  sim_list <- cleaned_list
}

start_x <- c()
start_y <- c()

for (i in 1:length(sim_list)) {
  start_x <- c(start_x, sim_list[[i]][1, 1])
  start_y <- c(start_y, sim_list[[i]][1, 2])
}

start_frame <- data.frame(
  ID = seq(1, length(start_x), 1), x = start_x,
  y = start_y, rad = sqrt(start_x^2 + start_y^2)
)

shist_plot <- ggplot(data = start_frame) +
  geom_freqpoly(aes(x = rad), bins = 10) +
  comtheme +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title = "Start Position Radii")

spos_plot <- ggplot(data = start_frame) +
  geom_point(aes(x = x, y = y)) +
  comtheme +
  coord_cartesian(xlim = c(-1, 1), ylim = c(-1, 1)) +
  labs(title = "Start Positions")

sx_plot <- ggplot(data = start_frame) +
  geom_freqpoly(aes(x = x), bins = 10) +
  comtheme +
  labs(title = "Start X")

sy_plot <- ggplot(data = start_frame) +
  geom_freqpoly(aes(x = y), bins = 10) +
  comtheme +
  labs(title = "Start Y")

end_x <- c()
end_y <- c()

for (i in 1:length(sim_list)) {
  end_x <- c(end_x, sim_list[[i]][nrow(sim_list[[i]]), 1])
  end_y <- c(end_y, sim_list[[i]][nrow(sim_list[[i]]), 2])
}

end_frame <- data.frame(ID = seq(1, length(end_x), 1), x = end_x, y = end_y, rad = sqrt(end_x^2 + end_y^2))

ehist_plot <- ggplot(data = end_frame) +
  geom_freqpoly(aes(x = rad), bins = 10) +
  comtheme +
  coord_cartesian(xlim = c(0, 1)) +
  labs(title = "End Position Radii")

epos_plot <- ggplot(data = end_frame) +
  geom_point(aes(x = x, y = y)) +
  comtheme +
  coord_cartesian(xlim = c(-1, 1), ylim = c(-1, 1)) +
  labs(title = "End Positions")

ex_plot <- ggplot(data = end_frame) +
  geom_freqpoly(aes(x = x), bins = 10) +
  comtheme +
  labs(title = "End X")

ey_plot <- ggplot(data = end_frame) +
  geom_freqpoly(aes(x = y), bins = 10) +
  comtheme +
  labs(title = "End Y")

grid.arrange(shist_plot, spos_plot, ehist_plot, epos_plot)

grid.arrange(sx_plot, sy_plot, ex_plot, ey_plot)
```


## chunk3, create a more robust data set w/ dist to start, to previous, and to 
origin (aka radius)

##Dependent on chunk1

```{r, echo = F}

time_interval <- 0.21

TBF <- sim_list
subTBF_nrow <- length(TBF[[1]][, 1])
time_seq <- matrix(seq(0, (subTBF_nrow - 1) * time_interval, time_interval), ncol = 1)
for (i in 1:length(TBF)) {
  TBF[[i]] <- cbind(TBF[[i]], time_seq)
  colnames(TBF[[i]]) <- c("x", "y", "is_bound", "time")
}

t_int <- TBF[[1]][, "time"][2]
d2svec <- c(0)
d2pvec <- c(0)
d2ovec <- c(0)
tot_d2o <- c()
d2_list <- vector("list", length(TBF))

for (i in 1:length(TBF)) {
  float_mat <- TBF[[i]]
  d2ovec[1] <- sqrt(float_mat[1, 1]^2 + float_mat[1, 2]^2)
  for (j in 2:nrow(float_mat)) {
    d2svec[j] <-
      sqrt((float_mat[1, 1] - float_mat[j, 1])^2 + (float_mat[1, 2] - float_mat[j, 2])^
        2)
    d2pvec[j] <-
      sqrt((float_mat[(j - 1), 1] - float_mat[j, 1])^2 + (float_mat[(j - 1), 2] - float_mat[j, 2])^
        2)
    d2ovec[j] <- sqrt(float_mat[j, 1]^2 + float_mat[j, 2]^2)
  }
  float_mat <-
    cbind(
      float_mat,
      matrix(d2svec, ncol = 1),
      matrix(d2pvec, ncol = 1),
      matrix(d2ovec, ncol = 1)
    )
  colnames(float_mat) <-
    c("x", "y", "is_bound", "time", "D2P", "D2S", "D2O")
  row.names(float_mat) <- c(1:nrow(float_mat))
  d2_list[[i]] <- float_mat
  tot_d2o <- c(tot_d2o, d2ovec)
}

plot(density(tot_d2o, from = 0, to = max(tot_d2o)))
```




## Chunk 4, visualize frequency of peripheral occupancy

## Dependent on chunk3
```{r, echo = F}

print_plots <- TRUE

periph_occu_list <- vector("list", length(d2_list))

bound_zone_thickness <-
  (1 - sqrt(2 / 3)) # this is outer third of nucleus

# # TODO maybe make binning a function? to apply across the list
# bin_to_10sec <- FALSE
#
for (i in 1:length(d2_list)) {
  float_po_logic <- d2_list[[i]][, "D2O"] > (1 - bound_zone_thickness)
  float_po_matrix <-
    matrix(seq(0, (length(float_po_logic) - 1) * time_interval, time_interval), ncol = 1)
  periph_occu_list[[i]] <-
    cbind(float_po_matrix, matrix(as.numeric(float_po_logic), ncol = 1))
}

preproc_NAs <-

  rep(NA, (length(periph_occu_list[[i]][, 1]) * length(periph_occu_list)))
po_plot_frame <-
  data.frame(
    Trajectory = preproc_NAs,
    time = preproc_NAs,
    is_periph = preproc_NAs
  )

for (i in 1:length(periph_occu_list)) {
  po_plot_frame[((i - 1) * nrow(periph_occu_list[[i]]) + 1):(i * nrow(periph_occu_list[[i]])), ] <-
    data.frame(
      Trajectory = i,
      time = periph_occu_list[[i]][, 1],
      is_periph = periph_occu_list[[i]][, 2]
    )
}

time_nrow <- length(unique(po_plot_frame$time))

float_time_interval <- po_plot_frame$time[2] - po_plot_frame$time[1]

mpp_frame <- po_plot_frame[po_plot_frame$time <= (float_time_interval * time_nrow), ]

order_mat <- matrix(nrow = length(unique(mpp_frame$Trajectory)), ncol = 2)

for (i in 1:length(unique(mpp_frame$Trajectory))) {
  float_pot <- mean(mpp_frame[mpp_frame$Trajectory == (unique(mpp_frame$Trajectory)[i]), "is_periph"])
  order_mat[i, ] <- c(i, float_pot)
}

new_order <- order(order_mat[, 2])

nompp_frame <- mutate(mpp_frame, rank = NA)

for (i in 1:length(unique(mpp_frame$Trajectory))) {
  temp_traj <- mpp_frame[mpp_frame$Trajectory == new_order[i], ]
  nompp_frame[(((i - 1) * nrow(temp_traj)) + 1):(i * nrow(temp_traj)), -(ncol(nompp_frame))] <- temp_traj
  nompp_frame[(((i - 1) * nrow(temp_traj)) + 1):(i * nrow(temp_traj)), (ncol(nompp_frame))] <- i
}

po_plot <- ggplot(data = nompp_frame) +
  geom_tile(aes(
    x = time,
    y = rank,
    color = is_periph,
    fill = is_periph
  ),
  position = "dodge"
  ) +
  scale_colour_viridis() +
  scale_fill_viridis() +
  coord_cartesian(xlim = c(0, (float_time_interval * time_nrow))) +
  comtheme


po_avg_time_frame <- data.frame(time = rep(NA, time_nrow), bound_frac = rep(NA, time_nrow))

for (i in 1:time_nrow) {
  cur_time <- float_time_interval * (i - 1)
  po_avg_time_frame[i, 1] <- cur_time
  po_avg_time_frame[i, 2] <- mean(mpp_frame[mpp_frame$time == cur_time, ]$is_periph)
}

pat_plot <- ggplot(data = po_avg_time_frame) +
  geom_point(aes(x = time, y = bound_frac * 100), alpha = 0.1) +
  stat_smooth(aes(x = time, y = bound_frac * 100)) +
  coord_cartesian(ylim = c(0, 100)) +
  comtheme +
  ylab("% of Trajectories at the periphery") +
  xlab("time (s)")

traj_vec <- unique(nompp_frame$Trajectory)

#TODO: Preallocate when not lazy 
vpat_frame <- data.frame(ID = numeric(), peri_perc = numeric())

for(i in 1:length(unique(nompp_frame$Trajectory))){
  float_traj <- traj_vec[i]
  float_frame <- nompp_frame[nompp_frame$Trajectory == float_traj,]
  vpat_frame[i,1]<-float_traj
  vpat_frame[i,2]<-sum(float_frame$is_periph)/nrow(float_frame)
}

vpat_plot <- ggplot(data = vpat_frame) +
  coord_cartesian(ylim = c(0,100))+
  geom_violin(aes(y = peri_perc * 100, x = "SIM"), fill = "yellow")+
  geom_errorbar(aes(ymax=mean(peri_perc)*100+sd(peri_perc)*100, ymin = mean(peri_perc)*100-sd(peri_perc)*100, x = "SIM"), width = 0.5)+
  geom_point(aes(y=mean(peri_perc)*100, x= "SIM"), color = "white", size = 4, shape = 19)+
  ylab("peripheral (% of time)")+
  comtheme

print(list_source_wd)

if (print_plots) {
  print(po_plot)
  print(vpat_plot)
  print(pat_plot)
}
```


## create list of last 200 steps in trajectory, quantify MSD, save individual MSD, plot MSD, 
and save merge MSD for subsequent plotting

##Dependent on chunk1

```{r MSD, echo=F, message=FALSE}

msd_dir <- "~/DataSets/trajectory_r_data/analytical_environment/calculated_MSD"
merge_dir <- "~/DataSets/trajectory_r_data/analytical_environment/MSD_merged"


for (i in 1:length(sim_list)) {
  if (i == 1) {
    msd_list <- vector(mode = "list", length = length(sim_list))
  }
  sl_len <- length(sim_list[[i]][, 1])
  msd_list[[i]] <- sim_list[[i]][((sl_len - 199):sl_len), ]
}

print(list_source_wd)
simMSD(msd_list, list_source_wd, output_dir = msd_dir)
kurzplot(list_source_wd, msd_input_dir = msd_dir, merge_output_dir = merge_dir)
```

```{r multimsd, echo = F, message = F}

mmsdplot(c(uap,gup))



```

##chunk5, repositioning
##

```{r Repositioning}
Repos_List <- d2_list
sim_lin()

tvv_frame <- data.frame(velocity = tvv)

velo_plot <- ggplot(data = tvv_frame) +
  geom_freqpoly(aes(x = velocity), bins = 30) +
  comtheme

time_plot <- ggplot(data = global_summary_sim) +
  geom_density(aes(x = time)) +
  coord_cartesian(xlim = c(0, max(global_summary_sim$time))) +
  comtheme

mdt_plot <- ggplot(data = global_summary_sim) +
  geom_density(aes(x = mean_delta_theta)) +
  comtheme

mdd_plot <- ggplot(data = global_direct_sim) +
  geom_freqpoly(aes(x = delta_dist), bins = 30) +
  comtheme

grid.arrange(velo_plot, time_plot, mdt_plot, mdd_plot)
```


##chunk 6, clusters

##Dependent on

```{r Clusters}
# randomize simlist into two pairwise lists

d2_list_length <- length(d2_list)

rand_d2 <- seq(1, d2_list_length, 1)

# peroform cluster component analysis on the two lists in a pairwise fashion
```

##chunck animate

#dependent on d2_list

```{r Animate}

save_product <- F

fname <- list_source_wd

d2len <- length(d2_list)
d2len <- 10
d2nrow <- nrow(d2_list[[1]])
d2ncol <- ncol(d2_list[[1]])

big_float_mat <- matrix(ncol = d2ncol + 1, nrow = d2nrow * d2len)

for (i in 1:d2len) {
  big_float_mat[((i - 1) * d2nrow + 1):(i * d2nrow), -(d2ncol + 1)] <- d2_list[[i]][1:d2nrow, 1:d2ncol]
  big_float_mat[((i - 1) * d2nrow + 1):(i * d2nrow), d2ncol + 1] <-
    rep(i, d2nrow)
}

float_frame <- as.data.frame(big_float_mat)

colnames(float_frame) <- c(colnames(d2_list[[1]]), "ID")

traj_anim <- ggplot(data = float_frame, aes(x = time, y = y, group = ID)) +
  coord_cartesian(ylim = c(-1, 1)) +
  geom_path(alpha = 0.25, size = 1) +
  # geom_point(alpha = 0.5)+
  comtheme +
  scale_color_viridis(discrete = F) +
  scale_fill_viridis(discrete = F) +
  labs(x = "time (s)", y = "Simulated Y position (micron)") +
  transition_reveal(time)

if (save_product) {
  animate(traj_anim, duration = 5, fps = 20, width = 1200, height = 600, renderer = gifski_renderer())
  anim_save(filename = paste(fname, ".gif", sep = ""), animaion = traj_anim, path = ".")
  # ggsave(paste(fname,".png",sep=""),width = 30, height = 15, units = "cm")
}
```
